On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-02-26 MS.tex
Change fig 3: RGR ideal vs RGR relaxed criteria Change fig4: RGR vs AGR under relaxed criteria Start change text

\subsection*{Main effects under ``ideal'' conditions}

Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal (and limited) numbers of observations between growth stages. We identified only 55 studies containing 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.

@@

\subsection*{Main effects under relaxed criteria}

We now report results from the entire dataset. Our aim is to determine if additional data alters or reinforces the above conclusions, by increasing replication. This entire dataset included correlations measured with both absolute growth rate and relative growth rate (Fig. \ref{fig:fig4}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e. traits could be measured on a different ontogenetic stage to growth data) or environmental conditions. The relaxed criteria considerably increased the number of replicates, from $n = 137$ to $n = 267$ correlations across 93 articles. However, the additional replicates were unequally distributed across trait-stage combinations. Some trait-stage combinations that already had a lot of data got even more support (e.g. from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates. On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: Wood density-seedling, maximum height-sapling, maximum height-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.

@@

For seed mass, we had hypothesized that the correlation between trait and growth rate would change if absolute growth rate was used instead of relative growth rate. Effect size for seed mass differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin. For other traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available.

>>>>

\subsection*{Main effects for relative growth rate under ``ideal'' conditions}

We identified only 55 studies containing 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species. Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal (and limited) numbers of observations between growth stages.

@@

\subsection*{Main effects for relative growth rate under relaxed criteria}

We now report results for relative growth rate from the entire dataset. Our aim is to determine if additional data alters or reinforces the above conclusions, by increasing replication. This entire dataset included correlations measured with both absolute growth rate and relative growth rate (Fig. \ref{fig:fig4}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e. traits could be measured on a different ontogenetic stage to growth data) or environmental conditions. The relaxed criteria considerably increased the number of replicates, from $n = 137$ to $n = 267$ correlations across 93 articles. However, the additional replicates were unequally distributed across trait-stage combinations. Some trait-stage combinations that already had a lot of data got even more support (e.g. from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates. On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: Wood density-seedling, maximum height-sapling, maximum height-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.

@@

\subsection*{Comparisons of relative and absolute growth rates under relaxed criteria}

For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available. Indeed for SLA
For seed mass, we had hypothesized that the correlation between trait and growth rate would change if absolute growth rate was used instead of relative growth rate. Effect size for seed mass differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.
